
Before introducing the class IP, we quickly remind (one of) the definition of the class NP.

\begin{defn}
    A language $L$ admits efficiently verifiable proofs if there exists a polynomial-time Turing machine $V$ that satisfies the following two properties: 
    \begin{description}\label{descr:np}
        \item[Completeness: ]for any $z \in L$ there is a string $\pi$ such that $V(z, \pi)$ returns 1 (i.e. $V$ "accepts").
        \item[Soundness: ]for any $z \notin L$ there is no string $\pi$ such that $V(z, \pi)$ accepts. 
    \end{description}~\cite{Algorithms}
\end{defn}

\begin{defn}
    The set of all languages $L$ with the properties of definition~\ref{descr:np} is denoted by the complexity class NP~\cite{randomness}.
\end{defn}


\subsection{The class IP}
The class IP is an extension of the class NP. Two key differences are introduced: first, we allow randomized verification procedure by relaxing the requirements of definition~\ref{descr:np}. Then we allow interactive verification, i.e. we introduce a prover and a verifier.
\begin{defn}
    Consider the following model:
    \begin{itemize}
        \item a deterministic unbounded time prover $P$,
        \item a randomized polynomial time verifier $V$,
        \item a pair of conversation tapes on which $P$ and $V$ exchange information.
    \end{itemize}
    An interactive proof system (IPS) for a language $L$, is a protocol between $P$ and $V$ where
    \begin{itemize}
        \item $P$ and $V$ are given an input $x$,
        \item through an exchange of messages, $P$ tries to prove to $V$ that $x \in L$,
        \item at the end of the interaction, $V$ outputs either "accept" if the proof is satisfactory or "reject" if not.
    \end{itemize}
    We require that
    \begin{description}
\item[completeness:] if both $P$ and $V$ follow the protocol and $x \in L$, then
$$
\operatorname{Pr}[V \text { accepts } x] \geq c,
$$
\item[soundness:] if $x \notin L$ and $V$ follows the protocol, then, regardless of what $P$ does,
$$
\operatorname{Pr}[V \text { accepts } x] \leq s.
$$
    \end{description}
    Where $c$ is the completeness parameter and $s$ is the soundness parameter. A common setting is to take $c=\frac{2}{3}$ and $s=\frac{1}{3}$~\cite{randomness}.
\end{defn}

\begin{defn}
    The class \textbf{IP} is the class of languages L such that there exists an IPS for L~\cite{randomness}.
\end{defn}
What does it mean? In an interactive proof a super powerful prover is trying to convince a skeptical and limited in computational power verifier that a string $z$, which is known to both, belong in the set $L$, even when it may be that in fact $z \notin L$. Because the verifier is interactively interrogating the prover he is able to reject false claims, that is determine with high statistical confidence if $z \in L$ or not. Crucial is the fact that the verifier is allowed to choose its messages to the prover, in a probabilistic and adaptive way.


An example of an IP problem is the \textsc{graph non-isomorphism} problem.

We can prove that~\cite{ipequalspspace}:
\begin{theorem}
    \begin{equation}
 \text{IP} = \text{PSPACE}.
    \end{equation}
\end{theorem}

Because of this we can verify the problems in PSPACE polynomially, using an interactive proof system as we already described.
We believe that the problems in PSPACE are significantly more difficult than those that can be checked using a deterministic proof, like NP problems.


